---
title: "CP1"
author: "Jianing Ren"
date: "09/09/2020"
output: html_document
---

## Loading Data
```{r,message=F}
activity=read.csv("/Users/rjn/OneDrive/大学/coursera/reproducible research/activity.csv")
library(tidyverse)
```

## What is mean total number of steps taken per day?

```{r}
day_total=aggregate(activity[,1],list(activity$date),sum)
hist(day_total$x,main="Distribution of Total Daily Steps")
mean(day_total$x,na.rm=T)
median(day_total$x,na.rm=T)
```

As Calculated above, the mean daily steps is 10766.19 and the median is 10765. 

## What is the average daily activity pattern?

```{r}
interval=activity%>%group_by(interval)%>%summarise(mean_steps=mean(steps,na.rm=T))
plot(interval$mean_steps,type="l")
interval[which(interval$mean_steps==max(interval$mean_steps)),]
```

Minutes 835-840 (about 2pm) has the maximum mean number of steps of about 206. 

## Filling NAs

```{r}
sum(is.na(activity$steps))
#There are 2304 total missing values here. I decide to fill those missing values with the interval means. 

filled=activity
for (i in 1:nrow(filled))
{
    if (is.na(filled[i,]$steps)==T)
        filled[i,]$steps=interval[which(interval$interval==filled[i,]$interval),]$mean_steps
}
```


```{r}
day_ttl_filled=aggregate(filled$steps,list(filled$date),sum)

hist(day_ttl_filled[,2])
mean(day_ttl_filled[,2])
median(day_ttl_filled[,2])
```

As compared to the original dataset, filling in the missing values doesn't change the histogram distribution and the centers much. 

## Weekday vs. Weekend Steps

```{r}
filled$is.weekday=weekdays(as.Date(filled$date))
filled$is.weekday=ifelse(filled$is.weekday %in% c("Saturday","Sunday"),"Weekend","Weekday")

interval2=filled%>%group_by(is.weekday,interval)%>%summarise(mean_steps=mean(steps))

ggplot(interval2,aes(x=interval,y=mean_steps))+geom_line()+facet_wrap(.~is.weekday)
```

